An Open-Source OpenSim Oculomotor Model for Kinematic and Dynamic Simulation

### 2018-07-09 doc/manuscript.tex
manuscript

he orbital plant consists of the globe (eyeball), three pairs of extraocular
muscles, and connective tissues. The size of an emmetropic human adult eye is
approximately 24.2 mm (transverse, horizontal) x 23.7 mm (sagittal, vertical) x
22.0–24.8 mm (axial, anteroposterior) with no significant difference between
sexes and age groups. In the transverse diameter, the eyeball size may vary from
21 mm to 27 mm. Thus, it can be approximated by a solid sphere with 12mm
radius. The eyeball was constructed in Blender, an open-source software 3D
creation Software. We used a spherical mesh with 32 segments and 12 rings, to
construct the vitreous humor (body) as solid sphere and a conical plate to
construct the cornea. The weight of an average human eye is 7.5grams and the
moment of inertia can be calculated similarly as in the case of a spherical
homogenous and isotropic object with radius 12mm ($\mat{I} = 2/5 m r^2$ at the
center of mass).

@@

\begin{table}[h]
  \caption{TODO}\label{tab:muscle-path}
  \begin{tabular}{@{}cccccccccc@{}}
    \toprule
    \textbf{Muscle} & \multicolumn{3}{c}{\textbf{Origin}}                                & \multicolumn{3}{c}{\textbf{Pulley}}                                & \multicolumn{3}{c}{\textbf{Insertion}}                                                                      \\ \midrule
                    & \textit{\textbf{Ox}} & \textit{\textbf{Oy}} & \textit{\textbf{Oz}} & \textit{\textbf{Px}} & \textit{\textbf{Py}} & \textit{\textbf{Pz}} & \textit{\textbf{Ix}} & \multicolumn{1}{l}{\textit{\textbf{Iy}}} & \multicolumn{1}{l}{\textit{\textbf{Iz}}} \\ \midrule
    LR              & -0.034               & 0.0006               & -0.013               & -0.0102              & 0.0003               & 0.012                & 0.0065               & \multicolumn{1}{l}{0}                    & \multicolumn{1}{l}{0.0101}               \\
    MR              & -0.030               & 0.0006               & -0.017               & -0.0053              & 0.00014              & -0.0146              & 0.0088               & \multicolumn{1}{l}{0}                    & \multicolumn{1}{l}{-0.0096}              \\
    SR              & -0.0317              & 0.0036               & -0.016               & -0.0092              & 0.012                & -0.002               & 0.0076               & 0.0104                                   & 0                                        \\
    IR              & -0.0317              & -0.0024              & -0.016               & -0.0042              & -0.0128              & -0.0042              & 0.00805              & -0.0102                                  & 0                                        \\
    SO              & 0.0082               & 0.0122               & -0.0152              & -0.030834            & 0.001145             & -0.01644             & 0.0044               & 0.011                                    & 0.0029                                   \\
    IS              & 0.0113               & -0.0154              & -0.0111
                    & -0.00718             & -0.0135              & 0
                                                                                         &
                                                                                           -0.008
                                                                                                                & 0                                        & 0.009 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{equation}\label{equ:passive-tissue}
  \vec{f}_t = -k_p \vec{q} - k_c 10^{-3} \vec{q}^3 - k_d * \vec{\dot{q}}
\end{equation}
%
where, $\vec{f}_t$ represents the passive tissue forces,
$k_p= 0.33 g / deg$ , $k_p= 1.56 g / (deg^3)$  (\hl{TODO: convert to
	$Nm / rad$}) and
$k_v= 10^{-4} Nm s / rad$ the constants and $\vec{\dot{q}} \inr{3}$ the
rotational coordinates of the model. These forces serve the eye’s stabilization,
and are modeled using \texttt{OpenSim}'s expression based coordinate force.
% 0.33 * 9.8066500286389 * 10**-3 / (numpy.pi / 180) = 0.18542028707494282
% 1.56 * 9.8066500286389 * 10**-3 / (numpy.pi / 180) ** 3 = 2877.4856893811248

>>>>

The orbital plant consists of the globe (eyeball), three pairs of extraocular
muscles, and connective tissues. The size of an emmetropic human adult eye is
approximately 24.2 mm (transverse, horizontal), 23.7 mm (sagittal, vertical),
22.0–24.8 mm (axial, anteroposterior) with no significant difference between
sexes and age groups. In the transverse diameter, the eyeball size may vary from
21 mm to 27 mm. Thus, it can be approximated by a solid sphere with 12 mm
radius. The eyeball was constructed in Blender, an open-source software 3D
creation Software. We used a spherical mesh with 32 segments and 12 rings, to
construct the vitreous humor (body) as solid sphere and a conical plate to
construct the cornea. The weight of an average human eye is 7.5 g and the
moment of inertia can be calculated similarly as in the case of a spherical
homogenous and isotropic object with radius 12 mm ($\mat{I} = 2/5 m r^2$ at the
center of mass).

@@

\begin{table}[h]
  \caption{TODO}\label{tab:muscle-path}
  \begin{tabular}{@{}cccccccccc@{}}
    \toprule
    \textbf{Muscle}
    & \multicolumn{3}{c}{\textbf{Origin}}
    & \multicolumn{3}{c}{\textbf{Pulley}}
    & \multicolumn{3}{c}{\textbf{Insertion}}
    \\ \midrule
    & \textit{\textbf{Ox}} & \textit{\textbf{Oy}} & \textit{\textbf{Oz}}
    & \textit{\textbf{Px}} & \textit{\textbf{Py}} & \textit{\textbf{Pz}}
    & \textit{\textbf{Ix}} & \textit{\textbf{Iy}} & \textit{\textbf{Iz}}
    \\ \midrule
    LR & -0.034 & 0.0006 & -0.013 & -0.0102 & 0.0003 & 0.012 & 0.0065 & 0 & 0.0101 \\
    MR & -0.030 & 0.0006 & -0.017 & -0.0053 & 0.00014 & -0.0146 & 0.0088 & 0 & -0.0096 \\
    SR & -0.0317 & 0.0036 & -0.016 & -0.0092 & 0.012 & -0.002 & 0.0076 & 0.0104 & 0 \\
    IR & -0.0317 & -0.0024 & -0.016 & -0.0042 & -0.0128 & -0.0042 & 0.00805 & -0.0102 & 0 \\
    SO & 0.0082 & 0.0122 & -0.0152 & -0.030834 & 0.001145 & -0.01644 & 0.0044 & 0.011 & 0.0029 \\
    IS & 0.0113 & -0.0154 & -0.0111 & -0.00718 & -0.0135 & 0 & -0.008 & 0 & 0.009 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{equation}\label{equ:passive-tissue}
  \vec{f}_t = -k_p \vec{q} - k_c 10^{-3} \vec{q}^3 - k_d * \vec{\dot{q}}
\end{equation}
% 
where, $\vec{f}_t$ represents the passive tissue forces, $k_p= 0.33$ g / deg,
$k_p= 1.56$ g / (deg^3) (\hl{TODO:convert to $Nm / rad$}) and $k_v= 10^{-4}$ Nm
s / rad the constants and $\vec{\dot{q}} \inr{3}$ the rotational coordinates of
the model. These forces serve the eye’s stabilization, and are modeled using
\texttt{OpenSim}'s expression based coordinate force.
% 0.33 * 9.8066500286389 * 10**-3 / (numpy.pi / 180) = 0.18542028707494282
% 1.56 * 9.8066500286389 * 10**-3 / (numpy.pi / 180) ** 3 = 2877.4856893811248
